\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2016-07-10 papers/jss-finalising/v71i02.tex
Summary: Murray at Google not Apple
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@954 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\author{Dirk Eddelbuettel\\Debian Project \And 
        Murray Stokely\\Apple, Inc. \And
        Jeroen Ooms\\University of California,\\Los Angeles}
\Plainauthor{Dirk Eddelbuettel, Murray Stokely, Jeroen Ooms}

@@

  Murray Stokely\\
  Apple, Inc.\\
  1 Infinite Loop\\
  Cupertino, CA, United States of America\\
  E-mail: \email{murray@stokely.org}\\
  URL: \url{http://www.stokely.org/}\\

>>>>

\author{Dirk Eddelbuettel\\Debian Project \And 
        Murray Stokely\\Google, Inc \And
        Jeroen Ooms\\University of California,\\Los Angeles}
\Plainauthor{Dirk Eddelbuettel, Murray Stokely, Jeroen Ooms}

@@

  Murray Stokely\\
  Google, Inc.\\
  1600 Amphitheatre Parkway\\
  Mountain View, CA, United States of America\\
  E-mail: \email{murray@stokely.org}\\
  URL: \url{http://www.stokely.org/}\\
